Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-20 report/absorption.tex
committing

The results for $\nu=10^{-2}$ (chosen as a parameter both in frequency and time domain) 
are shown in Figure \ref{fig:resonance_nu1e2} and for $\nu=10^{-3}$ in Figure \ref{resonance_nu1e3}. 
\begin{figure}

 \caption{In the }
 \label{fig:resonance_nu1e2}
\end{figure}

>>>>

The results for $\nu=10^{-2}$ (chosen as a parameter both in frequency and time domain) 
are shown in Figures \ref{fig:resonance_nu1e2_ex, fig:resonance_nu1e2_ey}. 
In the time domain, we chose the discretization size $\Delta x=0.025$. 
We display the harmonic dependence of the solution on time by fixing $x_c$ inside the domain and plotting 
$E_x^{\nu}(x_c,t)$ and $E_y^{\nu}(x_c, t)$. We compare these solutions to $\hat{E}_x^{\nu}(x_c)\mathrm{e}^{it}$ and 
$\hat{E}_y^{\nu}(x_c)\mathrm{e}^{it}$. In this case we choose $x_c=0$, where the resonance occurs. 
\begin{figure}

 \caption{In the left figure we show the dependence of the solutions $E_x^{\nu}(0,t)$ on time $t$. 
 In the right figure the solutions at time $t_c=...$ and $t_c=..$ are demonstrated and compared to
 $\Im{\hat{E}_y\mathrm{e}^{it}}$.
  \label{fig:resonance_nu1e2_ex}
\end{figure}

\begin{figure}

 \caption{In the left figure we show the dependence of the solutions $E_x^{\nu}(0,t)$ on time $t$. 
 In the right figure the solutions at time $t_c=...$ and $t_c=..$ are demonstrated and compared to
 $\Im{\hat{E}_y\mathrm{e}^{it}}$.
  \label{fig:resonance_nu1e2_ey}
\end{figure}
The $L_2$-error (\ref{eq:error}) on the time interval $()$ did not exceed $0.16$ for $E_x(x,t)$ and $0.085$ for $E_y(x,t)$.

### 2015-01-20 report/intro.tex
committing

\section{Introduction}

 In the case of heating devices for fusion experiment, for example, one can find itself dealing with what is called hybrid resonnance. Hybrid resonnance may cause Maxwell's equation with strong magnetic fields to develop singular solutions \textcolor{red}{insert refs}. The energy deposit is resonant and may exceed by far the energy exchange which occurs in Landau damping \textcolor{red}{ref}. Contrary to the Landau Dumping, however, hybrid resonnance appears in a simpler model coupling fluid equations with the non electrostatic part of Maxwell equations.
 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
 \begin{align}
 -\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
 \mu_0 \partial_t \Hbf + \curl\,  \E = 0
 \end{align}
 coupled with a linear current in two dimensions $\J = -eN_e \ubf_e$

 \[
 m_e \partial_t \ubf_e =-e (\E +\ubf_e \nabla B_0).
 \]
 Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current. We denote by $e$ the absolute value of the charge of elevtrons, 
  \begin{align*}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{align*}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions 
\begin{align*}
 H|_{-L}=g(t).
\end{align*}

\textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
\subsection{Boundary condition}
Robin Boundary condition at the left boundary of the domain
\be
-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \lambda\E_{inc} \wedge \n,
\ee
where  $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$

$curl \E = 0$ at the right boundary
\begin{remark}
When modelling antennas in plasma physics, in such applications as ITER, a good choice of boundary condition could be the use of $\lambda = \sqrt{alpha(-L)}$
\end{remark}
\textcolor{red}{!!!!!!!!!!!!}

>>>>

\section{Introduction}
In the case of heating devices for fusion experiment, for example, 
 one can find itself dealing with what is called hybrid resonnance. 
 Hybrid resonance may cause Maxwell's equation with strong magnetic 
 fields to develop singular solutions \textcolor{red}{insert refs}. 
 The energy deposit is resonant and may exceed by far the energy 
 exchange which occurs in Landau damping \textcolor{red}{ref}. 
 Contrary to the Landau Dumping, however, 
 hybrid resonnance appears in a simpler model coupling 
 fluid equations with the non electrostatic part of Maxwell equations.

 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
 \begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
\ee
Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current. We denote by $e<0$ the value of the charge of electrons and by $\m_e$ the electron mass0
\begin{align}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y\nonumber
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions
\begin{align*}
H|_{-L}=g(t).
\end{align*}
\textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
\subsection{Boundary condition}
Robin Boundary condition at the left boundary of the domain
\be
-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \lambda\E_{inc} \wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$
$curl \E = 0$ at the right boundary
\begin{remark}
When modelling antennas in plasma physics, in such applications as ITER, a good choice of boundary condition could be the use of $\lambda = \sqrt{alpha(-L)}$
\end{remark}
\textcolor{red}{!!!!!!!!!!!!}
